### 2019-02-19 sections/relatedwork.tex
minor fixes to related work

@@

% Our work differs in three major ways.
% First, we make an explicit distinction between the host language and the task
% language, to emphasise their boundaries.
% Second, we make use of separate semantic functions for querying the current task
% value, determining the continuation after an input event, and producing a user
% interface.
% In iTasks and its aforementioned semantics, these are integrated into the
% \CL{Task} datatype.
% Third, our system does not have the notion of task stability.
% When desired, stability can be introduced by the programmer, but the system
% itself makes no use of it.
% We argue that this does not impact the expressiveness of our language.

@@

Another similarity between \TOPHAT and process algebras, or any system with concurrency for that matter, is the need for synchronisation.
Broadly speaking, concurrency means that different parts of a program can interact with the environment independently, in an interleaved manner.
Synchronisation means that only some, but not all, of the possible interleavings are desirable.
The semantics of the step combinators in \TOPHAT, together with the fact that internal communication happens atomically, allows for concise TODO: say that synchronization in TOPHAT is the best.

Google Forms~\cite{googleforms} and Wufoo~\cite{wufoo} are web based survey administration apps that allows
users to compose forms and gather data from them. They are comparable to \TOP and
iTasks in that they provide an easy way for users to construct forms on the web.
However, Google Forms and Wufoo do not allow users to define what the system
then should do with this information, and can therefore not be regarded as a
workflow or business process modelling systems.

\subsection{Functional Reactive Programming}

@@

>>>>

\subsection{Task-oriented programming implementations}

@@

\paragraph{mTasks}
\fixme{Hier iets gezelligs over mTasks}
% Our work differs in three major ways.
% First, we make an explicit distinction between the host language and the task
% language, to emphasise their boundaries.
% Second, we make use of separate semantic functions for querying the current task
% value, determining the continuation after an input event, and producing a user
% interface.
% In iTasks and its aforementioned semantics, these are integrated into the
% \CL{Task} datatype.
% Third, our system does not have the notion of task stability.
% When desired, stability can be introduced by the programmer, but the system
% itself makes no use of it.
% We argue that this does not impact the expressiveness of our language.

@@

Another similarity between \TOPHAT and process algebras, or any system with concurrency for that matter, is the need for synchronisation.
Broadly speaking, concurrency means that different parts of a program can interact with the environment independently, in an interleaved manner.
Synchronisation means that only some, but not all, of the possible interleavings are desirable.
The semantics of the step combinators in \TOPHAT, together with the fact that internal communication happens atomically, allows for concise TODO: say that synchronisation in TOPHAT is the best.

\subsection{Reactive programming}

\paragraph{Esterel \& HipHop}

\paragraph{Functional reactive programming}

@@

Google Forms~\cite{googleforms} and SurveyMonkey~\cite{wufoo} (and their various other tools like Wufoo, Precise Polling and Zoomerang) are web based survey administration apps that allows
users to compose forms and gather data from them. They are comparable to \TOP and
iTasks in that they provide an easy way for users to construct forms on the web.
However, Google Forms and Wufoo do not allow users to define what the system
then should do with this information, and can therefore not be regarded as a
workflow or business process modelling systems.
